---
title: "Wildflower Experiment"
author: "Joanna Tang"
date: "12/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# CCBER Wildflower Experiment

```{r include = FALSE}

library(janitor)
library(lubridate)
library(rstatix)
library(FSA)
library(plotrix)
library(tidyverse)


wildflower <- read_csv("wildflower_data.csv") %>% clean_names()

```

## Seed Scarification Treatments
H1: Seed scarification treatment has an effect on the number of seedlings germinated.
Results: No significant difference in the number of seedlings germinated.  H1 not supported.
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Seeding Treatments

## Dataframe of LuBi, SiBe, LuSu
treated_species_df <- wildflower %>% 
  filter(species == "LuSu" | species == "SiBe" | species == "LuBi")

## Exploratory graphs
treated_hist <- treated_species_df %>% 
  ggplot() +
  geom_histogram(aes(x = number_of_seedlings))
#skewed right
treated_qq <- treated_species_df %>% 
  ggplot() +
  geom_qq(aes(sample = number_of_seedlings))
#skewed right


## Boxplots of seedlings per plot, by treatment, by species
treatment_box <- treated_species_df %>% 
  ggplot(aes(x = treated_untreated, y = number_of_seedlings)) +
  geom_boxplot() +
  geom_jitter(alpha = .4) +
  facet_wrap(~species) +
  labs(title = "Total number of germinated seedlings per plot, by scarification treatment", x = "Seed Treatment", y = "Seedlings (#)", caption = "Graph shows boxplots of total number of germinated seedlings in each plot.  \n No significant difference in scarification treatment on seedling germination exhibited in any of the species.") +
  theme_classic() +
  scale_y_continuous(expand = c(0,0), limits = c(0, 15)) +
  scale_x_discrete(labels = c("Scarification", "None"))
treatment_box

# Wilcoxon, for LuBi
lubi_untreated <- treated_species_df %>% 
  filter(species == "LuBi") %>% 
  filter(treated_untreated == "Untreated")
lubi_treated <- treated_species_df %>% 
  filter(species == "LuBi") %>% 
  filter(treated_untreated == "Treated")
lubi_treated_wilcox <- wilcox.test(lubi_treated$number_of_seedlings, lubi_untreated$number_of_seedlings)
#p = .715, W = 55

# Wilcoxon, for LuSu
lusu_untreated <- treated_species_df %>% 
  filter(species == "LuSu") %>% 
  filter(treated_untreated == "Untreated")
lusu_treated <- treated_species_df %>% 
  filter(species == "LuSu") %>% 
  filter(treated_untreated == "Treated")
lusu_treated_wilcox <- wilcox.test(lusu_treated$number_of_seedlings, lusu_untreated$number_of_seedlings)
#p = .1096, W = 71.5

```

## Caging Treatments
H2: Caging treatment has an effect on the number of seedlings germinated.
Results: Caging treatment only favored seedling germination of Lupinus succulentus.  H2 partially supported.
```{r echo = FALSE, message = FALSE, warning = FALSE}

# Caging Treatments

## Exploratory graphs
caging_hist <- wildflower %>% 
  ggplot() +
  geom_histogram(aes(x = number_of_seedlings))
#skewed right
caging_qq <- wildflower %>% 
  ggplot() +
  geom_qq(aes(sample = number_of_seedlings))
#skewed right


## Boxplots of seedlings per plot, by caging treatment, by species
caging_box <- wildflower %>% 
  filter(species != "NA") %>% 
  filter(species != "AnNu") %>% 
  filter(species != "SiBe") %>%
  filter(species != "CaMe") %>% 
  filter(species != "AcSt") %>% 
  ggplot(aes(x = caged_uncaged, y = number_of_seedlings)) +
  geom_boxplot(aes(fill = caged_uncaged), show.legend = FALSE) +
  geom_jitter(alpha = .4) +
  facet_wrap(~species) +
  labs(title = "Total number of germinated seedlings per plot, by caging treatment", x = "Caging Treatment", y = "Seedlings (#)", caption = "Graph shows boxplots of total number of germinated seedlings in each plot.  \n Caged plots favored Lupinus succulentus seedling germination (W = 84, p = 0.01).") +
  theme_classic()
caging_box

# Wilcoxon, for AcSt
acst_caged <- wildflower %>% 
  filter(species == "AcSt") %>% 
  filter(caged_uncaged == "Caged")
acst_uncaged <- wildflower %>% 
  filter(species == "AcSt") %>% 
  filter(caged_uncaged == "Uncaged")
acst_wilcox <- wilcox.test(acst_caged$number_of_seedlings, acst_uncaged$number_of_seedlings)
#p = .1983, W = 32.5

# Wilcoxon, for CaDe
cade_caged <- wildflower %>% 
  filter(species == "CaDe") %>% 
  filter(caged_uncaged == "Caged")
cade_uncaged <- wildflower %>% 
  filter(species == "CaDe") %>% 
  filter(caged_uncaged == "Uncaged")
cade_wilcox <- wilcox.test(cade_caged$number_of_seedlings, cade_uncaged$number_of_seedlings)
#p = .333, W = 37

# Wilcoxon, for LuBi
lubi_caged <- wildflower %>% 
  filter(species == "LuBi") %>% 
  filter(caged_uncaged == "Caged")
lubi_uncaged <- wildflower %>% 
  filter(species == "LuBi") %>% 
  filter(caged_uncaged == "Uncaged")
lubi_wilcox <- wilcox.test(lubi_caged$number_of_seedlings, lubi_uncaged$number_of_seedlings)
#p = .715, W = 45

# Wilcoxon, for LuSu
lusu_caged <- wildflower %>% 
  filter(species == "LuSu") %>% 
  filter(caged_uncaged == "Caged")
lusu_uncaged <- wildflower %>% 
  filter(species == "LuSu") %>% 
  filter(caged_uncaged == "Uncaged")
lusu_wilcox <- wilcox.test(lusu_caged$number_of_seedlings, lusu_uncaged$number_of_seedlings)
#p = .009221, W = 84

# Wilcoxon, for NuTe
nute_caged <- wildflower %>% 
  filter(species == "NuTe") %>% 
  filter(caged_uncaged == "Caged")
nute_uncaged <- wildflower %>% 
  filter(species == "NuTe") %>% 
  filter(caged_uncaged == "Uncaged")
nute_wilcox <- wilcox.test(nute_caged$number_of_seedlings, nute_uncaged$number_of_seedlings)
#p = .6473, W = 56

```

